RandomForest

### 2021-12-06 presentation.Rmd
representative tree fixe, new plot.
Fixed Presentation Representative tree

```{r}
rf_fit <- randomForest(as.factor(HeartDisease) ~ ., data = train, mtry = sqrt(ncol(train) - 1), importance = TRUE, type= "classification")

@@

## Representative Tree Paper

```{r}
reprtree:::plot.getTree(rf_fit)
```

>>>>

```{r}
rf_fit <- randomForest(as.factor(HeartDisease) ~ ., data = train, mtry = sqrt(ncol(train)-1), importance = TRUE, type= "classification")

@@

## Representative Tree

```{r}
reptree <- ReprTree(rf_fit, train, metric='d2')
plot(reptree, index=1)

### 2021-12-06 randomforest.Rmd
representative tree fixe, new plot.
Fixed Presentation Representative tree

@@

```{r}
plot(rf_fit)
```

@@

>>>>

set.seed(445)

library(leaps)
library(ISLR)
library(tidyverse) 
library(knitr)
library(glmnet) # package for lasso and ridge regression
library(pls)
library(ISLR)
library(ggpubr)
library(MASS)
library(splines)
library(gam)
library(tree)
library(randomForest)
library(gbm)
library(caret)
```

@@

@@

```{r}

reptree <- ReprTree(rf_fit, train, metric='d2')

```
```{r}

reptree$trees
plot(reptree, index=1)

```
```{r}
treet1 = predict(reptree, test, type = "class")

table(predicted = treet1, actual = test$HeartDisease)
```

```{r}

tree1 <- tree(HeartDisease~.,data= train)

plot(tree1)
text(tree1)

tree

```{r}
set.seed(445)

treet = predict(tree1, test, type = "class")

table(predicted = treet, actual = test$HeartDisease)

Overall test error rate (%83)
